\documentclass[10pt]{developercv}
\begin{document}
\begin{center}
    {\huge\textbf{\MakeUppercase{Antoine Barthelemy}}} \\
    \vspace{4pt}
    {\LARGE Site Reliability Engineer} \\
    \vspace{4pt}
	+33 695 450 611 \ \ antoine@linux.com \ \ \href{https://github.com/Ant0wan}{github.com/Ant0wan} \ \ Paris, France
\end{center}

\cvsect{Summary}
\hspace{0pt}
\begin{minipage}[t]{1.00\textwidth}
\vspace{0pt}
{Hi, I’m a Site Reliability Engineer and Developer with \textbf{over 4 years} of experience, focused on deploying and managing cloud infrastructure at scale. I’ve worked extensively with Kubernetes, AWS, and Terraform to build and maintain reliable, efficient systems. Lately, I’ve been honing in on optimizing system performance, improving CI/CD workflows, and ensuring high availability across multi-cloud environments.}
\end{minipage}
\vspace{6pt}
\hfill

\cvsect{Experience}

\begin{entrylist}
	\entry
		{Apr 2024 - Sep 2024}
		{\href{https://www.hublo.com/}{Hublo}}
		{Site Reliability Engineer}
		{Paris, France}
		{Deployed Kubernetes clusters on AWS for staging and production using Pulumi.
		Developed CI/CD pipelines and Helm charts for various applications, deployed with ArgoCD.
		Rationalized the AWS stack to reduce costs and simplify the infrastructure.}
		{AWS, ArgoCD, Datadog, GitHub Actions, Helm, Kubernetes, Pulumi, Postgresql}
	\entry
		{Jul 2023 - Nov 2023}
		{\href{https://craftedengineers.cloud/}{Cloud Crafted Engineers}}
		{Freelance Engineer}
		{Paris, France}
		{1st client: Developed automated network tests for a router operating system.
		2nd client: Co-designed an AWS cloud infrastructure, implementing feature deployments and CI/CD.}
		{AWS, Ansible, Github Actions, Kubernetes, KVM, Python, Terraform}
	\entry
		{Apr 2022 - Jun 2023}
		{\href{https://contentsquare.com/}{Contentsquare}}
		{Platform Engineer}
		{Rennes, France}
		{Managed multi-cloud deployments across Azure and AWS, optimizing cloud resources and maintaining high availability.
		Supported developers in delivering new features, services, and software releases while troubleshooting issues to ensure seamless operations.
		Assisted in improving the deployment of the monitoring stack.}
		{Ansible, AWS, Azure, Datadog, Github Actions, Go, Grafana, Helm, Jenkins, Kubernetes, PagerDuty, Prometheus, Python, Terraform, Vault}
	\entry
		{Jun 2021 - Jan 2022}
		{\href{https://sii-group.com/}{SII}}
		{DevOps Engineer}
		{Rennes, France}
		{Maintained 4GKE and implemented pull GitOps pipelines for Brittany-Ferries.}
		{FluxCD, GCP, GitlabCI, Istio, Kubernetes, Kustomize, SOPS, Terraform}
	\entry
		{Jul 2020 - May 2021}
		{\href{https://www.cil-lamballe.com/}{CIL}}
		{DevOps Engineer}
		{Lamballe, France}
		{\href{https://github.com/Ant0wan/VMWare-Kubenetes-cluster}{Deployed a HA Kubernetes cluster on bare metal servers} and migrated applications.}
		{Ansible, Bash, Centreon, Docker, Kubernetes, Linux, Rust, SQL, VMWare}
\end{entrylist}

\cvsect{Certifications}

\begin{entrylist}
	\certentry
		{Sep 2024}
		{\href{https://ti-user-certificates.s3.amazonaws.com/e0df7fbf-a057-42af-8a1f-590912be5460/e8d771bd-68bf-4ac7-8077-2e885178505a-antoine-barthelemy-21f9eeb4-ead2-4311-ba93-15865ca88f93-certificate.pdf}
		{Certified Kubernetes Administrator (CKA)}}
	\certentry
		{Mar 2024}
		{\href{https://ti-user-certificates.s3.amazonaws.com/e0df7fbf-a057-42af-8a1f-590912be5460/e8d771bd-68bf-4ac7-8077-2e885178505a-antoine-barthelemy-e9f7d66c-6134-4d58-9f70-9967859a7744-certificate.pdf}
		{Developing Helm Charts (SC104)}}
	\certentry
		{May 2023}
		{\href{https://www.credly.com/badges/7b8f2540-6b35-43a7-84d6-24dceb4001ee/public_url}
		{HashiCorp Certified: Terraform Associate (003)}}

\end{entrylist}

\cvsect{Education}

%\begin{entrylist}
%	\entry
%		{2018 - 2020}
%		{\href{https://42.fr/}{42}}
%		{Paris, France}
%		{\href{https://acclaim-production-app.files.credly.com/uploads/printable_pdf/printable_pdf/c858004e-df38-4309-b3c4-e814299c3c6e/42-Certificatepdf20241002-7-ngaeg7.pdf?response-content-disposition=attachment&X-Amz-Expires=604800&X-Amz-Date=20241002T173738Z&X-Amz-Algorithm=AWS4-HMAC-SHA256&X-Amz-Credential=AKIA5DGBWDLSBJ5BZX5Z\%2F20241002\%2Fus-east-1\%2Fs3\%2Faws4_request&X-Amz-SignedHeaders=host&X-Amz-Signature=a55bc0206580e9d1da963475100f2dcea13c7d6e9b855c452bca2ac1ecec216c}
%		{Certificate of Architect in Digital Technologies}}
%	\entry
%		{2014 - 2017}
%		{\href{https://www.essec.edu}{ESSEC}}
%		{Cergy, France}
%		{Bachelor of Business Administration}
%\end{entrylist}

\end{document}
