\documentclass[10pt]{developercv}
\begin{document}
\begin{center}
    {\huge\textbf{\MakeUppercase{Antoine Barthelemy}}} \\
    \vspace{4pt}
    {\LARGE Site Reliability Engineer} \\
    \vspace{4pt}
	+33 695 450 611 \ \ antoine@linux.com \ \ \href{https://github.com/Ant0wan}{github.com/Ant0wan} \ \ Paris, France
\end{center}

\cvsect{Summary}
\hspace{0pt}
\begin{minipage}[t]{1.00\textwidth}
\vspace{0pt}
{Hi, I’m a Site Reliability Engineer and Developer with \textbf{over 4 years} of experience, focused on deploying and managing cloud infrastructure at scale. I’ve worked extensively with Kubernetes, AWS, and Terraform to build and maintain reliable, efficient systems. Lately, I’ve been honing in on optimizing system performance, improving CI/CD workflows, and ensuring high availability across multi-cloud environments.}
\end{minipage}
\vspace{6pt}
\hfill

\cvsect{Experience}

\begin{entrylist}
	\entry
		{Apr 2024 - Sep 2024}
		{\href{https://www.hublo.com/}{Hublo}}
		{Site Reliability Engineer}
		{Paris, France}
		{Set up and scaled Kubernetes clusters on AWS using Pulumi for staging and production, migrating ECS clusters to Kubernetes namespaces. \ 
		Deployed an SFTP server, a CRM, various web applications, and data applications using Pulumi and Helm, enhancing build times for legacy applications. \ 
		Streamlined and secured AWS networking with security groups, peerings, and TLS, reducing costs and simplifying infrastructure management. \ 
		Automated deployment of Snowflake and Metabase with Terraform, developed Helm charts, and established a CI/CD pipeline for the data engineering team. \ 
		Configured a Network Load Balancer for managing layer 4 and layer 7 traffic for services.
		}
		{AWS, ArgoCD, Datadog, GitHub Actions, Helm, Kubernetes, Pulumi, Postgresql}
	\entry
		{Jul 2023 - Nov 2023}
		{\href{https://craftedengineers.cloud/}{Cloud Crafted Engineers}}
		{Freelance Engineer}
		{Paris, France}
		{6Wind - Contributed to a testing framework in Python and C to assess the load and functionality of a router OS. Executed tests on-premise using Ansible and KVM for durations of up to 8 hours.\\
		Lengow - Co-designed a scalable AWS cloud infrastructure to support feature deployment, established CI/CD services, and automated software release processes.
		}
		{AWS, Ansible, C, Github Actions, Kubernetes, KVM, Python, Terraform}
	\entry
		{Apr 2022 - Jun 2023}
		{\href{https://contentsquare.com/}{Contentsquare}}
		{Platform Engineer}
		{Rennes, France}
		{Led the refactoring of the Clickhouse Ansible deployment from Python 2.7 to Python 3.8 and built Ansible collections. \ 
		Contributed to a proof of concept for implementing Spinnaker to facilitate git-based workflows for Managed Delivery configurations. \ 
		Created a Python wrapper for Netflix Dispatch to enable quick deployment and scaling, serving as a PagerDuty replacement. \ 
		Actively managed multi-cloud deployments across Azure and AWS, optimizing cloud resources for high availability. \ 
		Collaborated with developers to support feature rollouts, troubleshoot issues, and maintain service reliability. \ 
		Contributed to several open-source projects, including Dispatch Netflix, Kibana Elasticsearch, Pritunl, Tfam, and Tfexe.
		}
		{Ansible, AWS, Azure, Datadog, Github Actions, Go, Grafana, Helm, Jenkins, Kubernetes, PagerDuty, Prometheus, Python, Terraform, Vault}
	\entry
		{Jun 2021 - Jan 2022}
		{\href{https://sii-group.com/}{SII}}
		{DevOps Engineer}
		{Rennes, France}
		{As the only DevOps engineer supporting a team of 12 developers, I managed four GKE clusters (about 5 nodes each), handling ~300 simultaneous users and maintaining their CI/CD pipelines for Brittany Ferries. \ 
		Led the migration of four terraformed GKE clusters to new infrastructure, incorporating FluxCD, ConfigConnector, Istio, and Sops.
		}
		{FluxCD, GCP, GitlabCI, Istio, Kubernetes, Kustomize, SOPS, Terraform}
	\entry
		{Jul 2020 - May 2021}
		{\href{https://www.cil-lamballe.com/}{CIL}}
		{DevOps Engineer}
		{Lamballe, France}
		{\href{https://github.com/Ant0wan/VMWare-Kubenetes-cluster}{Deployed a Kubernetes cluster on bare metal servers using Ansible.} \ 
		Upgraded VMware vSphere on all servers to enable Kubernetes Datastore support via VMware CNS API and CSI driver integration.
		}
		{Ansible, Bash, Centreon, Docker, Kubernetes, Linux, Rust, SQL, VMWare}
\end{entrylist}

\cvsect{Certifications}

\begin{entrylist}
	\certentry
		{Sep 2024}
		{\href{https://ti-user-certificates.s3.amazonaws.com/e0df7fbf-a057-42af-8a1f-590912be5460/e8d771bd-68bf-4ac7-8077-2e885178505a-antoine-barthelemy-21f9eeb4-ead2-4311-ba93-15865ca88f93-certificate.pdf}
		{Certified Kubernetes Administrator (CKA)}}
	\certentry
		{Mar 2024}
		{\href{https://ti-user-certificates.s3.amazonaws.com/e0df7fbf-a057-42af-8a1f-590912be5460/e8d771bd-68bf-4ac7-8077-2e885178505a-antoine-barthelemy-e9f7d66c-6134-4d58-9f70-9967859a7744-certificate.pdf}
		{Developing Helm Charts (SC104)}}
	\certentry
		{May 2023}
		{\href{https://www.credly.com/badges/7b8f2540-6b35-43a7-84d6-24dceb4001ee/public_url}
		{HashiCorp Certified: Terraform Associate (003)}}

\end{entrylist}

\cvsect{Education}

\begin{entrylist}
	\eduentry
		{Nov 2018 - Jun 2020}
		{\href{https://42.fr/}{42}}
		{Paris, France}
		{\href{https://acclaim-production-app.files.credly.com/uploads/printable_pdf/printable_pdf/c858004e-df38-4309-b3c4-e814299c3c6e/42-Certificatepdf20241002-7-ngaeg7.pdf?response-content-disposition=attachment&X-Amz-Expires=604800&X-Amz-Date=20241002T173738Z&X-Amz-Algorithm=AWS4-HMAC-SHA256&X-Amz-Credential=AKIA5DGBWDLSBJ5BZX5Z\%2F20241002\%2Fus-east-1\%2Fs3\%2Faws4_request&X-Amz-SignedHeaders=host&X-Amz-Signature=a55bc0206580e9d1da963475100f2dcea13c7d6e9b855c452bca2ac1ecec216c}
		{Certificate of Architect in Digital Technologies}}
	\eduentry
		{Sept 2014 - Feb 2017}
		{\href{https://www.essec.edu}{ESSEC}}
		{Cergy, France}
		{Bachelor of Business Administration}
\end{entrylist}

\end{document}
